Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-21 main.tex
improved inequality

\begin{lemma}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{\partial,p}
        \diam(T) \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where 
    \begin{align*}
        C_{\partial,p}
        \leq 
        \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
        .
    \end{align*}
    % \begin{align*}
    %     \| u \|_{L^{p}(T)}
    %     &
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla w \|_{\bfL^{p}(T)}
    %     +
    %     \| \gamma \|_{\bfL^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T)
    %     \| \nabla w \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} 
    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     .
    % \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{?}
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right) 
        \diam(T)^{p}
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The desired result follows. 
\end{proof}

@@

    We construct such a $u''_{m+1} \in W^{1,p}(T_{m+1})$ satisfying desirable bounds.
    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
    We define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi - u'_{m+1} \circ \Psi )$. 
    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$,
    and extend that $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
    By construction, $\hat g$ is the gradient of a unique function in $w \in W^{1,p}$ that vanishes at the boundary of $\hat U$,
    which satisfies Friedrichs inequality. In total, we utilize 
    \begin{gather*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        \| w \|_{L^{p}(\hat T)}
        ,
        \qquad 
        \| w \|_{L^{p}(\hat U)} 
        \leq 
        2 
        \| \hat g \|_{\bfL^{p}(\hat U)}
        ,
        \\
        \| \hat g \|_{\bfL^{p}(\hat U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{\bfL^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Dif \Psi_1)|^{-\frac 1 p} \cdot \| \Dif \Psi_1 \|
        \| \nabla u - \nabla u'_{m+1} \|_{\bfL^{p}(T)}
        .
    \end{gather*}
    We thus have
    \begin{align*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
        &
        \leq 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        2^{1+\frac n p}
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        \\&
        \leq 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        2^{1+\frac n p}
        \| \Dif \Psi \|
        \| \Dif \Psi \|
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        .
    \end{align*}
    We will also use the bound.  
\end{proof}

>>>>

\begin{lemma}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{\partial,p}
        \diam(T) \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where $C_{\partial,p} > 0$ is a constant such that 
    \begin{align*}
        C_{\partial,p}
        \leq 
        \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right),
        \quad 
        C_{\partial,p}
        \leq 
        2^{\frac n p}
        .
    \end{align*}
    % \begin{align*}
    %     \| u \|_{L^{p}(T)}
    %     &
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla w \|_{\bfL^{p}(T)}
    %     +
    %     \| \gamma \|_{\bfL^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T)
    %     \| \nabla w \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} 
    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     .
    % \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{?}
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right) 
        \diam(T)^{p}
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The first inequality follows.

    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
    We let $\hat u := u \circ \Psi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi )$. 
    Then $\nabla \hat u = \hat g$. 
    % 
    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordiante axes.
    We define $\tilde g = \nabla \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
    \begin{gather*}
        \| \tilde u \|_{L^{p}(\hat U)} 
        \leq 
        2 
        \| \tilde g \|_{\bfL^{p}(\hat U)}
        .
    \end{gather*}
    In addition to that, 
    \begin{gather*}
        \| u \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Dif \Psi)|^{\frac 1 p} 
        \| \hat u \|_{L^{p}(\hat T)}
        \leq 
        |\det(\Dif \Psi)|^{\frac 1 p} 
        \| \tilde u \|_{L^{p}(\hat U)}
        ,
        \\
        \| \tilde g \|_{\bfL^{p}(\hat U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{\bfL^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Dif \Psi_1)|^{-\frac 1 p} \| \Dif \Psi \| \cdot 
        \| \nabla u \|_{\bfL^{p}(T)}
        .
    \end{gather*}
    The second inequality follows.
\end{proof}

@@
